Fusing Filters with Integer Linear Programming

### 2014-04-18 2014betterfusionforfilters/Main.tex
intro: s/length/size/ so it matches "Size inference"

\begin{abstract}
Recent work on array fusion shows how to extract data-flow graphs from functional programs and compile them into efficient imperative loops. However, the compilation process only handles graphs that can be compiled into \emph{single} loops, and most programs require more. Prior work shows how use Integer Linear Programming (ILP) to \emph{cluster} the operators in a general data-flow graph into subgraphs that can be individually fused, but until now this approach did not handle operations like filter, which produce arrays of a different length than their input. We extend the existing ILP approach with support for length changing operators, using an external ILP solver to find good clusterings.
\end{abstract}

>>>>

\begin{abstract}
Recent work on array fusion shows how to extract data-flow graphs from functional programs and compile them into efficient imperative loops. However, the compilation process only handles graphs that can be compiled into \emph{single} loops, and most programs require more. Prior work shows how use Integer Linear Programming (ILP) to \emph{cluster} the operators in a general data-flow graph into subgraphs that can be individually fused, but until now this approach did not handle operations like filter, which produce arrays of a different size than their input. We extend the existing ILP approach with support for size changing operators, using an external ILP solver to find good clusterings.
\end{abstract}

### 2014-04-18 2014betterfusionforfilters/section/01-Introduction.tex
intro: s/length/size/ so it matches "Size inference"

In Figure~\ref{f:normalize2-cluterings}, the dotted lines show possible clusterings of operators. Stream fusion implicitly choses the solution on the left as its compilation process cannot fuse a produced array into multiple consumers. The best existing ILP approach will chose the solution on the right as it cannot cluster operators that consume arrays of different lengths. Our system choses the solution in the middle, which is also optimal for this example.

% NOTE: This set of bullets needs to fit on the first page, without spilling to the second.
Our contributions are as follows:
\begin{itemize}
\item   
We extend prior work by Megiddo~\cite{megiddo1998optimal} and Darte~\cite{darte2002contraction}, with support for length changing operators. Length changing operators can be clustered with the operators that generate their source arrays, and compiled naturally with data-flow fusion (\S\ref{s:ILP}).

>>>>

In Figure~\ref{f:normalize2-cluterings}, the dotted lines show possible clusterings of operators. Stream fusion implicitly choses the solution on the left as its compilation process cannot fuse a produced array into multiple consumers. The best existing ILP approach will chose the solution on the right as it cannot cluster operators that consume arrays of different sizes. Our system choses the solution in the middle, which is also optimal for this example.

% NOTE: This set of bullets needs to fit on the first page, without spilling to the second.
Our contributions are as follows:
\begin{itemize}
\item   
We extend prior work by Megiddo~\cite{megiddo1998optimal} and Darte~\cite{darte2002contraction}, with support for size changing operators. Size changing operators can be clustered with the operators that generate their source arrays, and compiled naturally with data-flow fusion (\S\ref{s:ILP}).
